### 2021-08-13 doc/thesis/chapters/results.tex
impl_time_analysis plot

%%%%%%%%%%%%%%%%%%%%
\subsection{Interfaces}

@@

%%%%%%%%%%%%%%%%%%%%
\subsection{Audio Output}

@@

%%%%%%%%%%%%%%%%%%%%
\subsection{Lines of Code}

@@

%%%%%%%%%%%%%%%%%%%%
\subsection{Implementation Time}

@@

\subsubsection{AXI Stream Inferface}

@@

\subsubsection{AXI4-Lite Interface}

@@

\subsubsection{Registers}

@@

\subsubsection{FIR Filter}

@@

\subsubsection{Sample Decimation}

@@

\subsubsection{Receiver Structure}

@@

Sim speed of x min of recorded FM signal\\
Sim speed of x min of recorded FM signal\\
Sim speed of x min of recorded FM signal\\
Sim speed of x min of recorded FM signal\\
Sim speed of x min of recorded FM signal\\
Sim speed of x min of recorded FM signal\\
Sim speed of x min of recorded FM signal\\
Sim speed of x min of recorded FM signal\\
Sim speed of x min of recorded FM signal\\

%
% VHDL:
%          time                samples
%   audio         sim        in      out
%  0.1000 s    73:44 min  (96000 -> 4000)
%  0.0100 s    09:37 min  ( 9600 ->  400)
%  0.0025 s    02:36 min  ( 2400 ->  100)
%
% HLS:
%
%
% Matlab:
%          time                samples
%   audio         sim        in      out
%  1.7 s    0.45 sec     1632000   68000
%

@@

%%%%%%%%%%%%%%%%%%%%
\subsection{Integration}
% - IP generation and integration into Vivado
% - Another manual step in VHDL is the addition of the AXI bus interfaces to the IP.
% - Issue: HLS driver import did not work - Vivado SDK is a mess (bad UI based on Eclipse, has bugs, no error output, etc...)

%%%%%%%%%%%%%%%%%%%%
\subsection{Hardware Utilization}
% --> utilization reports

%%%%%%%%%%%%%%%%%%%%
\subsection{Latency}
% --> utilization reports

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Interfaces}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Audio Output}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Lines of Code}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Implementation Time}

@@

%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{AXI Stream Inferface}

@@

%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{AXI4-Lite Interface}

@@

%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Registers}

@@

%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{FIR Filter}

@@

%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Sample Decimation}

@@

%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Receiver Structure}

@@

Sim speed of x min of recorded FM signal\\

measurements are always including loading of data, running through DUT and storing the results.
exclusively result analysis, since this is shared and thus taking the same amount of time.
several measurements are done multiple times, to achieve a good average result, that is independent of the current processor load of the host PC.

Figure \ref{fig:impl_time_analysis} shows something
%
% VHDL:
%          time                   samples
%   audio         sim           in      out
%  0.1000 s    73:44 min       96000 -> 4000
%  0.0100 s    09:37 min        9600 ->  400
%  0.0025 s    02:36 min        2400 ->  100
%
% HLS:
%          time                   samples
%   audio         sim           in      out
%     0.8 s    00:17 min       768000 -> 32000
%     1.7 s    00:36 min      1632000 -> 68000
%
%
% Matlab:
%          time                   samples
%   audio         sim           in      out
%     1.7 s  00:00:00.52 min   1632000   68000
%

\includepicture [0.55] [0, trim=10 20 10 10, clip] {The implementation time of the implementation variants. Note the logarithmic scale of the y-axis.} {impl_time_analysis} {img/matlab/impl_time_analysis}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Integration}
% - IP generation and integration into Vivado
% - Another manual step in VHDL is the addition of the AXI bus interfaces to the IP.
% - Issue: HLS driver import did not work - Vivado SDK is a mess (bad UI based on Eclipse, has bugs, no error output, etc...)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Hardware Utilization}
% --> utilization reports

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Latency}
% --> utilization reports
